RSA Project paper

### 2016-11-28 Paper/Paper.tex
paper update

\renewcommand\labelenumi{\Roman{enumi}}
\begin{enumerate}
\item \textit{Choosing B:} 
\end{enumerate}

\subsection {Problems we met \& the solutions}

\subsection {Tables and Graphs of Experiments}
\end{document}

>>>>

\renewcommand\labelenumi{\Roman{enumi}}
\begin{enumerate}
\item \textit{Choosing B \& M:} \vspace{2mm}
\\ We read a lot of resources and most of them suggests a value between $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$ and $\exp{(2\sqrt{\log{n}\log{\log{n}}})}$, The reason why choose it this way, an explanation is in the appendix A of Contini's paper \cite{contini}. At first in class professor emphasis that the number is just a toy number, therefore, we are using the smaller bound $\exp{(\frac{1}{2}\sqrt{\log{n}\log{\log{n}}})}$. And then, we use  this bound to test our number, the result is 1.4 million and the factor base size is about 50 thousands. But we use pollard rho found a small factor, and we reduce the original number by dividing this factor which is 809. And we calculate again it became 970000+, and our factor base is shrink to 40 thousands. For the convenience of communication, we choose 1 million as our B.

For choosing M, we do not really know any formulas or suggestions from the resources we read. Our M is just based our experiments. Our main idea is to set M is large enough, and we continuously searching until, we found enough relations. In our experiment we set M to 2 trillion, which means we are searching 4 trillion numbers.

\item \textit{Building Factor Base:} \vspace{2mm}
\\ To build the factor base, first we need to generate primes. There are several ways to do it. Our approach build a prime generator by Eratosthenes Sieve. we used a dictionary to dynamically hold the relations. For example, if a test number, is not in the dictionary then it is a prime, and then add the square of this number to the dictionary. if the test number in the dictionary, then, pull out all its factors and add the sum of the test number and its factor to the dictionary. after that, delete the test number from the dictionary. Then, we use this generator to build our factor base, if the prime build by generator satisfy two conditions which are less than $B$ and makes $N$ be the quadratic residue, then add it to our factor base, otherwise, continue generating until the prime greater than our $B$. The good part of this method is that the building process is very fast, the cons is that it use extra memory to save the relations.

To decide whether $\legendre{N}{p} = 1$, we implemented both Euler criterion and Legendre Symbol. And probably because our factor base was not enough, we did not notice Legendre Symbol is much faster than Euler Criterion. Since professor suggest us use Legendre Symbol, we are using Legendre symbol to test $\legendre{N}{p}$.

\item \textit{Pre-Sieving:} \vspace{2mm}
\\ In this stage, we did a lot optimizations. First, we use array as dictionary, which means we use prime value as array's index, since our B is one million, our array length is one million. The reason why we do this is we need extremely fast in our sieving process, since array get operation is $\mathcal{O}(1)$. And the downside is obviously wasting memory. Then, we use this approach to save 3 informations. First one, is the roots of quadratic residue. Since every odd prime has two solutions, we use a two dimension array to save both. And we also cache the value of $\log p$, Since we do not want any unnecessary calculations in our sieving process. And finally, we also store the offset of x from the start position $\lfloor \sqrt{N} \rfloor - M$, i did not see any resources mentioned this, but we think it is useful, since we can very easily obtain the smooth number by just add offset to start position.

And here is a story about how math help us solve problems. As we motioned before, we want save the info of the offset of x from the start position, which is also find the closest position from x that satisfy $x+o \equiv r \pmod{p}$ where $x$ is start position $o$ is offset, and $r$ is the square roots of quadratic residue. And we want find $o$, at very first we use a very naive way to do it, since $x+o=r+ip$ where $i \in \{0,1,\dots\}$ we just keep increasing i until we found a value makes two side equal. And then we found this approach was very slow when the factor base is getting bigger (we used to choose a much smaller factor base). Then, we just sit down and wrote down the formula and analysis. And we realize if we want the $o$, it is just simply $o = r-x \pmod{p}$. After we use this new approach the program runs 2 times faster than before. Then we think, do a math analysis before writing code is probably a good idea.

\item \textit{Sieving:} \vspace{2mm}
\\ The sieving array is to store the accumulated $\log{p}$ value for each position in the range of [$-M, M$]. Therefore, its length is $2M+1$. The sieving process is just go through each prime in our factor base. Get its position which already cached in previous stage, and add $r+ip$ where $r$ is the position to the sieve array.

This stage is probably most simple part of our program. It is not the idea is simple, it is made to be simple, since this is the bottle neck of our whole program. if we made this process calculates more, the program will slow down dramatically. And we also did this part in parallel. Not only multi-thread but also multi-process.

We implemented a sever which only responsible to generate job which specify the range to search and add it to a task queue. And then, each client connected to sever and got job from the queue. The job could be very large, so we split the job according to the memory of client, and starting multi-thread according to the number of processors of client, and sieving.

\item \textit{Save Sieving Result:}
\item \textit{Build Exponent Matrix:}
\item \textit{Finding Null Space:}
\item \textit{Calculating Factors:}

\end{enumerate}

\subsection {Results of Experiments}

\pagebreak
\begin{thebibliography}{99}

\bibitem{contini} Scott Patrick Contini, [\textit{Factoring Integers with the Self-Initializing Quadratic Sieve}], 1997

\end{thebibliography}

\end{document}
